Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling

### 2019-12-23 lloveras_2020.tex
..

%---------REMOVE THESE OPTIONS AND DEFs BEFORE SUMBISSION---------------------------------------
\usepackage[usenames,dvipsnames]{xcolor} % Las opciones: [USENAMES,DVIPSNAMES] 
                                         % ponen a disposición los colores ejemplificados aquí:
                                         % https://en.wikibooks.org/wiki/LaTeX/Colors
\def\diego#1{\textcolor{red}{#1}}
\def\albert#1{\textcolor{blue}{#1}}
\def\fede#1{\textcolor{ForestGreen}{#1}}
\def\temp#1{\textcolor{gray}{#1}}
\def\notebyalbert#1{\textcolor{blue}{NOTE: #1}}
%-----------------------------------------------------------------------------------------------

@@

\temp{DEMT has been improved since the previously published work. We now perform hollow-tomography with the EUV images, (definir hollow-tom) and a 3D regularized of the solution was applyed to obtain smother and more reliable result at the edge of the tomographic grid.} \albert{NOTA de Albert: Explicá que hacés sin justificarte. Luego aclará como se hizo eso en trabajos previos, y cual es el impacto esperado. Puedo proveer un párrafo de ejemplo, pero creo que será mejor que vos escribas como te salga y yo luego edito. Algo muy importante para todo el paper: proponete escribir ``párrafos modulares". Es decir que, con las razonables limitaciones, puedan moverse de lugar, de orden, y sigan funcionando. No definiría hollow-tomography, es un término coloquial interno nuestro. Lo correcto es que al hablar de datos mucho más arribas expliques que los datos del disco no se utilizan, pero no le des un nombre a la tomografía.}

@@

Thermal conduction power is calculated by the Spitzer model \citep{spitzer_1962}, which describes coronal plasma regime properly. The thermal conduction power is obtained by taking the divergence of the conductive loss function $F_c(s)=-\kappa_0\,{T(s)}^{5/2}\,\frac{dT}{ds}(s)$, where $\kappa_0 = 9.2 \times 10^{-7}  {\rm erg\,sec^{-1}\,K^{-7/2}}$ is the Spitzer thermal conductivity. Due in coronal regime, the plasma is confined to the magnetic field, thus conduction is also predominately in the magnetic field direction. Thus, divergence is only the derivative along the position $s$:

\begin{equation}\label{Ec}
E_c(s)=\frac{1}{A(s)}\,\frac{d}{ds}\left[A(s)\,F_c(s)\right].
\end{equation}

\noindent
where $A(s)$ represent the magnetic flux tube area along the position $s$.

@@

Taking into acount the null divergence condition of magnetic field, the model integrate, between tomographic limits, each power quantities over magnetic flux tube independently of its area. Therefore, a loop-integrated equation for the energy flux balance is obtained ($[\rm{erg\,sec^{-1}\,cm^{-2}}]$):

\begin{equation}\label{FluxBalance}
\phi_h = \phi_r + \phi_c.
\end{equation}

\noindent
where $\phi_{h,r,c}$ are the loop-integrated energy input flux, radiative flux and conductive flux for each magnetic field line at 1.025 $R_{\odot}$.

For a complete description of the energy balance model, the reader can refer to \citet{maccormack_2017}.
We compute the loop-integrated energy quantities for both rotation analyzed in this work. 
\\

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/Grispoint_2082_demt_paper_test_Rpoint-map.pdf}
\includegraphics[width=0.495\textwidth,clip=]{figs/Grispoint_2208_demt_paper_test_Rpoint-map.pdf}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_full_Rpoint-map.pdf}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_awsom_paper_Rpoint-map.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_full_Rpoint-map.pdf}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_awsom_paper_Rpoint-map.eps}
\caption{\diego{At the top, latitude-longitude location of all open (grey) and closed (black) lines traced. At the bottom, latitude-longitude location of each leg that was traced and that meets the criteria listed in Section \ref{trace}. Type 0, I, II and III are shown in blue, red, violet and green respectively at $1.105\,\mrsun$ for CR-2082 (left panel) and CR-2208 (right panel). See Section \ref{trace} for a definition of the different types of {legs}.} \notebyalbert{(by ALBERT) The population of DOWN LEGS in CR-2008 is negligible. These are VERY SMALL loops, I am pretty sure but you and Ceci shoudl check it.} }
\label{rpoint_demt}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_ne_1055.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_lambda_n.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_Tm.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_Tm.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_Tm.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_Tm.eps}
\caption{{Statistical distribution of DEMT results traced along legs of type 0, I, II and III (from top to bottom), as defined in Section \ref{trace}. From left to right: electron density at the coronal base $\NCB\equiv\sqravgN(r=1.055\,\mrsun)$, electron density scale height $\lN$, and loop-averaged electron temperature $\aTm$. Results for target rotations CR2082 and CR2208 are shown in blue and red color, respectively. In each panel the median value $m$ is indicated.} \notebyalbert{The histogram Figures in this draft need to be improved, in particular font size-and-type need to be optimized for clear reading. Also, we need to improve their X/Y ratio, here I stretched the Y size a bit in the LaTeX source.}}
\label{histos_fulldemt}
\end{center}
\end{figure}

@@

\begin{figure}[ht]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2082_ccdownenergia.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2208_ccdownenergia.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2082_ccenergia.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2208_ccenergia.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2082_cgenergia.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2208_cgenergia.eps}
\caption{\diego{Statistical results of the loop integrated energy flux quantities $\phi_r,\phi_c,$ and $\phi_h$ in colors blue, red and green, respectively for CR-2082 (left) and CR-2208 (right). From top to left loops of type 0, I and II where both legs meets the criteria from Section \ref{trace}.} \notebyalbert{The type-0 population in CR-22208 is negligible. These are VERY SMALL loops, I am pretty sure but you and Ceci shoudl check it. This can explain the non-physical $\phi_h<0$ population.} \notebyalbert{Utilizar los colores del paper de Cecilia, notar que el conductivo debe ser el verde y el energy input flux (h) debe ser el rojo. De paso, haría el verde un poco menos chillón, como en el paper de Ceci, se verá mejor. En el XYOUTS podés poner la letra griega $\phi$,  y para que te salga r,c,h como subíndice pero no pequeño usá: ``!Dp!N", donde p=r,c,h.}}
\label{energia_demt}
\end{center}
\end{figure}

The frequency histograms of Figure \ref{energia_demt} shows the loops-integrated energy quantities: $\phi_h$, $\phi_r$ and $\phi_c$ in green, blue, and red lines respectively, for both rotations.

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Ne_demt_awsom_2082_1105.eps}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Ne_demt_awsom_2208_1105.eps}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Te_demt_awsom_2082_1105.eps}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Te_demt_awsom_2208_1105.eps}
\caption{Longitude-averaged latitudinal dependence of the electron density (top) and temperature (bottom) for DEMT (blue) and AWSoM (red) results at $1.105\,\mrsun$. The left (right) panels correspond to CR-2082 (CR2208). The vertical black line indicates the longitude-averaged latitudes of the open/close magnetic boundary.}
\label{perf_lat}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2082_up.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2082_up.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2208_up.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2208_up.eps}
\caption{{Average fits to $\Ne(r)$ (left panels) and $T_e(r)$ (right panels) for legs of type I (red), II (violet), and III (green), for CR-2082 (top panel) and CR-2208 (bottom panel). Solid lines correspond to DEMT results while dashed lines correspond to AWSoM results.}}
\label{perfiles_promedio}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_Tm.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_Tm.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_Tm.eps}
\caption{{Statistical distribution of DEMT (blue) and AWSoM (red) results traced along legs of type I, II and III (from top to bottom), as defined in Section 2.3. From left to right: electron density at the coronal base $\NCB\equiv \Ne(r=1.055\,\mrsun)$\diego{en realidad Ncb se define distinto para awsom que demt.}, electron density scale height $\lN$, and leg-averaged electron temperature $\aTm$. In each panel the median value $m$ is indicated.}}
\label{histos_2082}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Vr_2082_5995.eps}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Vr_2208_5995.eps}
\caption{{Longitude-averaged latitudinal dependence of the AWSoM model wind speed at $6\,\mrsun$ for CR2082 (left panel) and CR2208 (right panel).}}
\label{perf_lon_vr}
\end{center}
\end{figure}

@@

\noindent\notebyalbert{Antes de enviar esto a Michigan se precisa un conjunto de conclusiones compacto y claro. Creo que yo las pondría en tres grupos: a) conclusiones DEMT solas (esto incluye estructura termodinámica, up/down loops, energía), b) comparación AWSoM/DEMT (la clobal, es decir promedio longitudinal, y la que difernecia estructuras magnéticas), c) Wind Speed y Densidad basal.}

>>>>

%---------REMOVE THESE OPTIONS AND DEFs BEFORE SUMBISSION---------------------------------------
\usepackage[usenames,dvipsnames]{xcolor} % Las opciones: [USENAMES,DVIPSNAMES] 
                                         % ponen a disposición los colores ejemplificados aquí:
                                         % https://en.wikibooks.org/wiki/LaTeX/Colors
\def\diego#1{\textcolor{red}{#1}}
\def\albert#1{\textcolor{orange}{#1}}
\def\fede#1{\textcolor{ForestGreen}{#1}}
\def\temp#1{\textcolor{gray}{#1}}
\def\notebyalbert#1{\textcolor{blue}{NOTE: #1}}
%-----------------------------------------------------------------------------------------------

@@

\temp{DEMT has been improved since the previously published work. We now perform hollow-tomography with the EUV images, (definir hollow-tom) and a 3D regularized of the solution was applyed to obtain smother and more reliable result at the edge of the tomographic grid.} \notebyalbert{NOTA de Albert: Explicá que hacés sin justificarte. Luego aclará como se hizo eso en trabajos previos, y cual es el impacto esperado. Puedo proveer un párrafo de ejemplo, pero creo que será mejor que vos escribas como te salga y yo luego edito. Algo muy importante para todo el paper: proponete escribir ``párrafos modulares". Es decir que, con las razonables limitaciones, puedan moverse de lugar, de orden, y sigan funcionando. No definiría hollow-tomography, es un término coloquial interno nuestro. Lo correcto es que al hablar de datos mucho más arribas expliques que los datos del disco no se utilizan, pero no le des un nombre a la tomografía.}

@@

\noindent\notebyalbert{Trabajé todo lo naranja. Primero decidí que es mejor no numerar $E_c$ sino $F_c$. Eso te quedará claro cuando agregues las ecuaciones (11) y (12) que te indico más abajo y leas el último párrafo naranja de abajo, ahí cierra todo. Además describí que son los $\phi$ en forma correcta. El texto previo estaba muy flojón, entre otras cosas se hablaba de una (inexistente) ``conductive loss function" y de una (incorrectamente denominada) ``area along the loop". Obviamente luego de chequear este texto naranja borrá esta nota azul en particular.}

\albert{The thermal conduction power $E_c$ equals the divergence of the conductive heat flux $F_c$, i.e.
$E_c(s)=[1/A(s)]\,{\rm d}[A(s)\,F_c(s)]/{\rm d}s$, where $A(s)$ is the transversal area of the magnetic flux tube at position $s$. Under a quiescent solar corona plasma regime, the conductive flux is assumed to be dominated by the electron thermal conduction, described by the usual Spitzer model \citep{spitzer_1962}
\begin{equation}\label{Fc}
F_c(s)=-\kappa_0\,{T(s)}^{5/2}\,\frac{dT}{ds}(s),
\end{equation}
where $\kappa_0 = 9.2 \times 10^{-7}  {\rm erg\,sec^{-1}\,K^{-7/2}}$ is the Spitzer thermal conductivity.}

@@

\albert{The energy balance given by Equation (\ref{Balance}) is then integrated in the volume of any given coronal magnetic flux tube. Dividing the result by the flux tube ara at the coronal base, and making use of the soleidonal conditon of the magnetic field, a field-line integrated version of that energy balance is found,
\begin{equation}\label{FluxBalance}
\phi_h = \phi_r + \phi_c.
\end{equation}
\noindent
where the line integrated flux quantities $\phi_{r,c}\,[\rm{erg\,sec^{-1}\,cm^{-2}}]$ are given by \citep{maccormack_2017},}\\
\notebyalbert{Diego, please include here Equations (11) and (12) of that paper, which incredibly enough will have the same numbers here.}

\albert{Note that, for any given field line, all quantities in these two expresions can be computed from the DEMT and AWSoM models through Equations (\ref{Fc})-(\ref{Er}). Once computed, the quantity $\phi_h$ can be calculated, which is the enery input flux required at the coronal base of each coronal field-line required to mantain a stable coronal structure.}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/Grispoint_2082_demt_paper_test_Rpoint-map.pdf}
\includegraphics[width=0.495\textwidth,clip=]{figs/Grispoint_2208_demt_paper_test_Rpoint-map.pdf}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_full_Rpoint-map.pdf}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_awsom_paper_Rpoint-map.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_full_Rpoint-map.pdf}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_awsom_paper_Rpoint-map.eps}
\caption{\albert{\emph{Top panels:} latitude-longitude location at heliocentric height $r=1.105\,\mrsun$ of all open (grey) and closed (black) traced field lines for which there are along at least five DEMT data points, for both CR2082 (left) and CR2208 (right). \emph{Bottom panels}, latitude-longitude location (at the same height) of each traced leg that meets the criteria listed in Section \ref{trace}. Type 0, I, II and III legs (see text) are shown in blue, red, violet and green, respectively, for CR-2082 (left) and CR-2208 (right).}}
\label{rpoint_demt}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_ne_1055.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_lambda_n.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_Tm.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_Tm.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_Tm.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_Tm.eps}
\caption{{Statistical distribution of DEMT results traced along legs of type 0, I, II and III (from top to bottom), as defined in Section \ref{trace}. From left to right: electron density at the coronal base $\NCB\equiv\sqravgN(r=1.055\,\mrsun)$, electron density scale height $\lN$, and loop-averaged electron temperature $\aTm$. Results for target rotations CR2082 and CR2208 are shown in blue and red color, respectively. In each panel the median value $m$ is indicated.} \notebyalbert{ (by Albert) The histogram Figures in this draft need to be improved, in particular font size-and-type need to be optimized for clear reading. Also, we need to improve their X/Y ratio, here I stretched the Y size a bit in the LaTeX source.} \albert{Also, I believe you should use a FIXED x-range for each quantity (one for $\NCB$, one for $\lambda_N$ and one for $\aTm$) accross all Figures 5, 12, and 13, as that will visually highlinght how meadians and standard deviations compare, both between targets (CR2082 versus CR2208, this Figure) as well as between models (DEMT versus AWSoM, Figures 12 and 13).}}
\label{histos_fulldemt}
\end{center}
\end{figure}

@@

\begin{figure}[ht]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2082_ccdownenergia.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2208_ccdownenergia.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2082_ccenergia.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2208_ccenergia.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2082_cgenergia.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2208_cgenergia.eps}
\caption{\albert{Statistical results of the loop-integrated energy flux quantities $\phi_r,\phi_c,$ and $\phi_h$ in colors blue, red and green, respectively for CR-2082 (left) and CR-2208 (right). From top to bottom, panels show the results for loops of type 0, I and II, which are loops for which both legs meet the criteria from Section \ref{trace}.} \notebyalbert{(by Albert) En el XYOUTS podés poner la letra griega $\phi$ usando los comandos ``!4" y ``!3",  y para que te salga r,c,h como subíndice pero no tan pequeño usá: ``!Dp!N", dónde p=r,c,h.}}
\label{energia_demt}
\end{center}
\end{figure}

\albert{For both target rotations, and for loops of type 0, I and II, Figure \ref{energia_demt} shows the frequency histogram of the loop-integrated energy flux quantities $\phi_h$, $\phi_r$ and $\phi_c$ in green, blue and red color, respectively.}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Ne_demt_awsom_2082_1105.eps}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Ne_demt_awsom_2208_1105.eps}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Te_demt_awsom_2082_1105.eps}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Te_demt_awsom_2208_1105.eps}
\caption{Longitude-averaged latitudinal dependence of the electron density (top) and temperature (bottom) for DEMT (blue) and AWSoM (red) results at $1.105\,\mrsun$. The left (right) panels correspond to CR-2082 (CR2208). The vertical black line indicates the longitude-averaged latitudes of the open/close magnetic boundary in both hemispheres. \notebyalbert{(by Albert): The idea of this Figure is to show how DEMT and AWSoM compare AS A FUNCTION OF LATITUDE at an intermediate height of the DMET grid, averaged in longitude (excluding zones with ARs).}}
\label{perf_lat}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2082_up.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2082_up.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2208_up.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2208_up.eps}
\caption{{Average fits to $\Ne(r)$ (left panels) and $T_e(r)$ (right panels) for legs of type I (red), II (violet), and III (green), for CR-2082 (top panels) and CR-2208 (bottom panels). Solid lines correspond to DEMT results while dashed lines correspond to AWSoM results.} \notebyalbert{(by Albert): The idea of this Figure is to show how DEMT and AWSoM compare AS A FUNCTION OF HEIGHT, in three distinct types of magnetic structures, and for both rotations.}}
\label{perfiles_promedio}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_Tm.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_Tm.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_Tm.eps}
\caption{{Statistical distribution of DEMT (blue) and AWSoM (red) results traced along legs of type I, II and III (from top to bottom), as defined in Section 2.3. From left to right: electron density at the lowest coronal height of the AWSoM model $\Ne(r=1.055\,\mrsun)$, electron density scale height $\lN$, and leg-averaged electron temperature $\aTm$. In each panel the median value $m$ is indicated.}}
\label{histos_2082}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Vr_2082_5995.eps}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Vr_2208_5995.eps}
\caption{{Longitude-averaged latitudinal dependence of the AWSoM model wind speed at $6.0\,\mrsun$ for CR2082 (left panel) and CR2208 (right panel).} \notebyalbert{(by Albert): Even if this is not yet the terminal speed, it is a pretty high height, and one can already see the transition from FAST to SLOW speed in the model, where the abslute minimum indicates the location of the HCS at this height. I believe it is interesting to compare these two curves with Figure 10. Note that while in this Figure all latitudes are magnetically open, in Figure 10 only the part at latitudes larger than the vertical black lines are open. Note that DEMT shows that in the open low corona $N_e$ dereases from the O/C boundary towards the poles, anti-correlating with the AWSoM terminal speed, which is nice. In order to quantify this anti-correlation we need to trace the termnal speed and the DEMT $N_e$, which we may need to do with the help of Chip and Nishtha. Chip, we can discuss this idea over Skype after Xmas if you are around.}}
\label{perf_lon_vr}
\end{center}
\end{figure}

@@

\noindent\notebyalbert{(by Albert) This section will discuss and summarize some main conclusions, possibly in three groups: a) DEMT analysis alone (including thermodynamical structure, up/down loops, energy considerations, etc.), b) Comparison AWSoM/DEMT (longitude-averaged latitudinal profiles, height-dependence profiles in different magnetic structures, etc), and c) Correlation betweem AWSoM terminal wind speed and DEMT basal density, I will expand on this later this week as this may require help from Michigan).}
